---
title: "Effsize Text vs. Viz - Pilot Study I"
subtitle: "Reproducible Documentation of Analysis"
format: 
  html:
    toc: true
    theme: flatly
    fontsize: .8em
---

## Import of the already cleaned data

```{r}
library(tidyverse)
library(GGally)
library(skimr)

data_pilot01 <- 
  read_delim("Data/TextViz.csv", delim = ";")|> 
  # compute survey duration
  mutate(survey_duration = dmy_hm(ended) - dmy_hm(created)) |> 
  # rename true effect sizes
  mutate(text_effect_size_1 = effect_size_7,
         text_effect_size_2 = effect_size_8,
         text_effect_size_3 = effect_size_9,
         text_effect_size_4 = effect_size_10,
         text_effect_size_5 = effect_size_11,
         text_effect_size_6 = effect_size_12,
         plot_effect_size_1 = effect_size_1,
         plot_effect_size_2 = effect_size_2,
         plot_effect_size_3 = effect_size_3,
         plot_effect_size_4 = effect_size_4,
         plot_effect_size_5 = effect_size_5,
         plot_effect_size_6 = effect_size_6) |> 
  # deselect old true effect size variables
  select(-starts_with("effect_size_"))

glimpse(data_pilot01)
skimr::skim(data_pilot01)
```

## Participant Behaviour

### Survey Duration

```{r}
data_pilot01  |> 
  ggplot(aes(survey_duration)) +
  geom_histogram() +
  theme_minimal()
```

## Results of Attention and Comprehension checks

```{r}
data_pilot01 |> 
  select(attention_check_1a, attention_check_1b,
         check_graph2, check_test, check_text2) |> 
  skim()
```

## Data Wrangling Wide to Long Format

It is important to know that `effect_size1` to `effect_size6` encode the true effect sizes of the shown plots. `effect_size7` to `effect_size12` encode the true effect sizes of the shown **text.**

First we have to wrangle a table like this:

| session | stimulus_type | stimulus_number | true_effectsize | first_stim | perceived_diff | perceived_PS | perceived_inf | perceived_rel |
|--------|--------|--------|--------|--------|--------|--------|--------|--------|
| a       | plot          | 1               | .8              | plot_first |                |              |               |               |
| b       | text          | 1               | .2              | text_first |                |              |               |               |
| c       | plot          | 1               | -.5             | plot_first |                |              |               |               |

The variable `first_stim` is only reconstuctable by the time stamps. So let's wrangle the first four columns:

```{r}
data_maxlong <- 
  data_pilot01 |> 
  select(session,
         starts_with("plot_"),
         starts_with("text_")) |> 
  pivot_longer(cols = -session,
               names_to = "variable",
               values_to = "value") |> 
  mutate(stimulus_type = str_sub(variable, 1, 4),
         nth_stimulus_per_type = str_sub(variable, -2, -1),
         nth_stimulus_per_type = case_when(nth_stimulus_per_type == "_1" ~ 1,
                                           nth_stimulus_per_type == "_2" ~ 2,
                                           nth_stimulus_per_type == "_3" ~ 3,
                                           nth_stimulus_per_type == "_4" ~ 4,
                                           nth_stimulus_per_type == "_5" ~ 5,
                                           nth_stimulus_per_type == "_6" ~ 6,
                                           nth_stimulus_per_type == "_7" ~ 7,
                                           nth_stimulus_per_type == "_8" ~ 8,
                                           nth_stimulus_per_type == "_9" ~ 9,
                                           nth_stimulus_per_type == "10" ~ 10,
                                           nth_stimulus_per_type == "11" ~ 11,
                                           nth_stimulus_per_type == "12" ~ 12), 
         measurement = case_when(str_detect(variable, "accuracy") ~ "probability_of_sup",
                                 str_detect(variable, "effect_size") ~ "effect_size",
                                 str_detect(variable, "informativity") ~ "informativity",
                                 str_detect(variable, "relevance") ~ "relevance",
                                 str_detect(variable, "informativity") ~ "informativity",
                                 str_detect(variable, "difficulty") ~ "difficulty",
                                 str_detect(variable, "informativity") ~ "informativity",
                                 T ~ "Attention: Error in Code"))

data_long <- 
  data_maxlong |> 
  select(-variable) |> 
  pivot_wider(id_cols = c(session, stimulus_type, nth_stimulus_per_type),
              names_from = measurement,
              values_from = value) 

skim(data_long)  
```

## Research Questions

RQ 1: How accurate (dependent variable 1), efficient (dependent variable 2), informative (dependent variable 3) and relevant (dependent variable 4) are graphically and textually presented effect sizes received by teachers?

RQ 2: Are there differences between the display modes (graph vs. text) in relation to the four dependent variables?

## Statistical Analyses

Concerning Research Question 1, part

1:

2:

3: How informative are graphically and textually presented effect sizes?
```{r}

overall_mean_informativity_plot <- data_maxlong |>  filter(str_detect(variable, "^plot_perceived_informativity_")) |>  summarize(mean_value = mean(value, na.rm = TRUE))

overall_mean_informativity_text <- data_maxlong |>  filter(str_detect(variable, "^text_perceived_informativity_")) |>  summarize(mean_value = mean(value, na.rm = TRUE))

# Create a data frame with the summary statistics

summary_data <- data.frame( Variable = c("Plot Informativity", "Text Informativity"), Mean_Value = c( overall_mean_informativity_plot$mean_value,  overall_mean_informativity_text$mean_value ) )

# Create a horizontal bar plot with values on the x-axis

ggplot(summary_data, aes(x = Mean_Value, y = Variable, fill = Variable)) + geom_bar(stat = "identity") + labs(title = "Mean Values by Variable and Aspect", x = "Mean Value") + theme_minimal() + theme(axis.text.y = element_text(hjust = 0))

```


Concerning Research Question 2
